Better fusion for filters

### 2014-04-04 2014betterfusionforfilters/section/01-Introduction.tex
suggest normalise2 for better motivating program?

@@

The reduction of the clustering problem to integer linear programming was previously described by \cite{megiddo1998optimal}, though they do not consider filtering operations.

>>>>

\TODO{This program has filters and other interesting stuff, but doesn't have ``multiple unique best solutions''}
\begin{code}
 normalize2 :: Array Int -> Array Int
 normalize2 us
  = let sum1 = fold   (+) 0 us      (A1) (S1) (I1)
        gts  = filter (>0)  us      (A1) (S2) (I1)
        sum2 = fold   (+) 0 gts     (A1) (S2) (I2)
        nor1 = map  (/sum1) us      (A2) (S3) (I3)
        nor2 = map  (/sum2) us      (A2) (S4) (I3)
    in (nor1, nor2)
\end{code}
Our approach, @A1-A2@, requires only two loops for this particular case.
Stream fusion (@S1-S4@) is unable to fuse @sum1@ and @gts@ together, as there is nothing to be inlined between them, so requires four whole traversals of the input array, @us@.
Similarly, existing imperative solutions (@I1-I3@) would be unable to fuse @gts@ and @sum2@ together, as the iteration size is completely different.

@@

The reduction of the clustering problem to integer linear programming was previously described by\cite{megiddo1998optimal}, though they do not consider filtering operations.
